Plant species traits and growth rates: meta-analysis shows correlations change with plant size as predicted

### 2015-07-30 MS.tex
Change according to reviwers comments (different graph and new paragraph)

\item 
Traits should influence growth in a way that depend on individual plants size. We outline mechanisms and hypotheses based on new theory, and test these predictions for five traits using a meta-analysis of 112 studies (\textgreater{} 500 correlations).

@@

Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}. Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when  potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}. At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover (see Text Box 1\ref{sec:growth}).

Here, we review published literature reporting on relationships between
plant growth and five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea,  maximum height= Hmax, and seed mass= SM), in order to assess the following questions.

@@

The main effect of increased seed size is to produce a larger overall seedling. Generally relative growth rate decreases with size, and as such larger seedlings are predicted to have a lower relative growth rate during the earliest phases of growth \citet{Turnbull:2012ew}. However, among larger plants we expect the effect of this initial size to be minimal, and thus the correlation between seed size and growth rate should disappear.

@@

@@

We aimed to identify studies that measured the correlation between a functional trait and a growth measurement, and searched for relevant studies using a three step procedure. First, we identified traits for which a substantial number of studies would be available, using a literature snapshot in Web of Science. While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Beckmann:2012hn}. This limitation does not apply to Google Scholar, where, theoretically, all text that is electronically available on the Internet will be indexed. Thus, our second step was to systematically read documents returned by Google scholar for a restricted set of traits. Finally, we identified and recorded other possible data sources using our own knowledge as researchers in the field. (This included adding data from an as-yet unpublished study by Gleason et al). The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.

@@

We focused on an initial list of 20 traits (Fig. \ref{Fig1}): the five for which we had prior expectations, plus 15 others which capture different aspects of plant species strategies. Specific leaf area (SLA), leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and assimilation rate of CO$_2$ (Aarea) are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}. Seed mass (SM), and maximum plant height (Hmax) capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}. Wood density (WD) and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy \citep{Chave:2009iy}. Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}. Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf \citep{Lambers:1992bj}. We used the literature snapshot to identify traits which i) were most likely to return a substantial number of articles , and ii) shared a large proportion of their literature list with other traits. The Web of Science database (Thomson Reuters) was searched between March and June 2014 using a range of Boolean search terms in English. Search terms were as follows: (``NAME'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), ``NAME'' was one of trait names listed in

@@

Across the 112 article used in our meta-analyses, plants were categorized into four stages according to the expertise and the apprciation of the authors (i.e.seedling, juvenile, sapling, adult). 
While by compiling data across multiple studies there is a risk of assigning plants of similar size to different categories, the thershold size is standardized for a plant stage across the 112 studies ().

When the stage information was not explicitly given, data were recorded as 'mix'.

Second, we re-assigned plants to three stage categories ("juvenile", "sapling" and "adult") according to size and age cutoffs established by looking at the range values observed across all the 112 studies (Fig. \ref{FigA1}). We preferred the term "juvenile" to "seedling", because for a portion of the scientific community "seedling" also refers to a particular experimental condition (a greenhouse experiment). Overall, the different studies were largely consistent in their classification of plants into "juvenile", "sapling" and "adult" groups  (Fig. \ref{FigA1}). In particular, there was a clear break between juveniles and saplings in both age (at 1 yr) and height (at 0.5m); there was also a clear break between saplings and adults in diameter (at 10cm). The distinctions between sapling-adult in age and height, and between seedling-sapling in diameter were less pronounced. To ensure consistency across studies we used simple allometric relationships from the Biomass And Allometry Database (BAAD) \citep{Falster:2015} to match between age, diameter and height ranges for each stage category (Fig. \ref{FigA2}).

Thus, we established the following rules: i) `juveniles' are plants of {[}0,0.5) m in height , or {[}0,0.2{]} cm in diameter, or $\leq$ 1 yrs old; ii) `saplings' are plants of {[}0.5-5{]} m , or (0.2,10{]} cm in diameter, or (1-30{]} yrs, and iii) `adult' are plants \textgreater{}5 m in height, or \textgreater{}10 cm in diameter, or \textgreater{} 30 yrs and/or in the reproductive stage. We attributed the study to a new stage category when 95\% of the recorded range of sizes for that study lay within the new category. We attributed a study to the adult stage when the authors identified the plants as reproductive regardless the plant size or age.

In the main text we report the results using the second approach, i.e. standardized categories. Results using the first approach are similar and are available in Fig. \ref{FigA8}.

@@

We tested size/stage effect on traits for which \textgreater{}20 correlation coefficients across at least two stages were recorded. We used a mixed-effect model of meta-analysis, in which it is assumed that studies within a stage share a common mean effect but that there is also random variation among studies in a stage, in addition to sampling variation. This random effect allows us to account for the heterogeneity among studies (e.g.~experimental type, vegetation type, error, etc.). For each trait, we established if stage could explain variance in the coefficient correlation by comparing models with the stage variable to the null model using log-likelihood ratios \citep{Zuur:2009cfa}. If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the null model. Effects of other variables (vegetation type, experiment type and growth measurement) were also tested individually (results shown in the Fig. \ref{FigA8}). Estimates of the effect size for each stage were considered significant if the 95\% confidence intervals did not overlap with zero. In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size. Finally, we checked the dataset for publication bias with funnel plots (\citealt{Koricheva:2013tz}, Fig. \ref{FigA9}). A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect. In addition, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a `failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value.

@@

For both SLA and SM, the correlation between growth rate and the trait  changed significantly with plant size in the manner expected. Model fits improved when stage was incorporated (see log likelihood ratio tests, Fig. \ref{Fig2} a and d; average values for the coefficients r ($r_{\textrm{mean}}$) in Fig. \ref{FigA5}). The correlation between growth and SLA shifted from strongly positive at juvenile stage $r_{\textrm{mean}}=0.6 \pm 0.08$, Mean +SD) to not significantly different from zero at adult stage ($r_{\textrm{mean}}= -0.01 \pm 0.07$, CI 95\% overlapping zero in Fig. \ref{Fig2} a). The correlation between growth and SM shifted from negative at juvenile stage ($r_{\textrm{mean}}= -0.59 \pm 0.07$) to not significantly different from zero at adult stage ($r_{\textrm{mean}}= -0.09 \pm 0.02$, , CI 95\% overlapping zero in Fig. \ref{Fig2} d). For both traits,  correlation coefficients recorded at sapling stage were intermediate between juvenile and adult stages.

@@

Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results. The results reported were confined to correlations across species and under non-stressed conditions. A "complete" dataset (n=328 vs n=198) also included correlations measured at within-species level, and under stressed conditions, and spanning different plant stages. This "complete" dataset generated similar effect sizes to those reported above from the "ideal" dataset, and led to similar conclusions (Fig. \ref{Fig2} grey points). Differences concerned often the confidence intervals around particular mean effect sizes in Fig. 2. These differences in CI were not easily attributed to any single cause. For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct};  these correlations unlike others used wood density values from adult plants together with growth from juveniles. For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 7 correlations measured under low light conditions were added. Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig. \ref{FigA7}) .

@@

We found 112 studies published between between 1983 and 2014 that met our requirements. Climate zones spanned from temperate regions to  tropics (map in Fig. \ref{FigA3}). Different experiment types (laboratory, field, plantation or greenhouse) and growth measurements were included (see Fig. \ref{FigA8} for analyses of how these factors affected  correlations between growth and traits). Given this variety, it was not surprising to find wide ranges of r reported for all traits. For instance,  r varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for WD (Fig. \ref{FigA4}). Number of species used for each correlation ranged from 1 to 300 species with average  31. As expected the correlation coefficient varied less widely as sample size increased (funnel plots Fig. \ref{FigA9}). In the analyses described in Figs 2, A5 and A6 coefficients were weighted according to sample size, making the small-sample extremes less influential. Funnel plots exhibited a typical funnel shape for all five functional traits analyzed, showing no evidence for publication bias (Fig. \ref{FigA9}).

@@

The meta-analysis reported here demonstrates that the influence of traits on growth rates changes as plants grow from small to large, for several key traits. Plant growth rates change with size through ontogeny  \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd} - \textit{they follow a trajectory of growth} - and species traits should be understood as influencing this trajectory and consequently rearranging the ranking of growth rates with size, rather than as rendering species fast-growing or slow-growing throughout life.

@@

It has previously been noted that the correlation of SLA with growth disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), and this meta-analysis generalises that result. Several authors have suggested that the disappearance of SLA's influence on growth is associated with increasing total leaf area \citep{Reich:1992wm,Poorter:2008iu,Wright:2010tp}. In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf and other tissues turnovers, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.

@@

\begin{figure}[htbp]
\centering
\includegraphics{output/Fig1.pdf}
\caption{\textbf{Number of correlations between trait and growth for each plant stage recorded in our dataset.} Shown here are \textcolor{red}{'raw} dataset' (recorded at both interspecific and intraspecific level, under unstressed and stressed conditions). Bar colors: red for adult, orange for sapling, grey for juvenile. Aarea (or Amass) = rate of $CO_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax= asymptotic maximum height,  Ks =stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density}
\label{Fig1}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/Fig2.pdf}
\caption{\textbf{The relationship between growth rates and SLA or seed mass changes with plant stage.} Plots show the effect size (+ 95\%CI) of the correlation \textcolor{red}{across species} between growth rate and five functional traits for plant stage comparisons. \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Asymptotic height (Hmax) \textbf{d)} Seed mass and \textbf{e)} Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero. Black point: ideal data (under unstressed conditions), grey points: all the data. 'n' indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT, for ideal data only) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means the stage model fitted the data better than the null model.
}
\label{Fig2}
\end{figure}

@@

\begin{itemize}
  \item "code.zip": the data and analysis code used to generate the results in this paper. A copy of the complete data set is also available from the Dryad Digital Repository.
\end{itemize}

@@

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA1.pdf}
\caption{\textbf{Range of plant size in \textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter and their assigned plant stage} Each segment represents the plant size range addressed in our dataset. ID is the reference number of the article in our dataset. The colors represents the stage information given by the authors (green: seedling, blue:juvenile, orange: sapling, red: adult, grey: mix), and the vertical line the limit we choose to established our stage categories. Shown here are the \textcolor{red}{"raw} dataset" (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions). }
\label{FigA1}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA2.pdf}
\caption{\textbf{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database}. Green and red lines are the cutoffs between stage categories used in the meta-analyses. Green lines corresponds to limits between juveniles and saplings, red lines to limits between saplings and adults.}
\label{FigA2}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA3.pdf}
\caption{\textbf{Geographical distribution of site locations from studies performed in the field used in the meta-analysis.} Shown here are the \textcolor{red}{"raw} dataset" (recorded at both interspecific and intraspecific level and under unstressed and stressed conditions).}
\label{FigA3}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA4.pdf}
\caption{\textbf{Range of the correlation of correlations (r) between
growth and trait \textcolor{red}{from 112 articles}.} Coefficients of correlation (r)
between the plant growth and \textbf{a)} Specific leaf area (SLA, n=
111), \textbf{b)} Wood density (WD, n=64), \textbf{c)} Asymptotic
maximum height (Hmax, n=23), \textbf{d)} Seed mass (Seedmass, n=36 and
\textbf{e)} Rate of CO2 assimilation (Aarea, n=24) reported from 112
articles. \textcolor{red} {The x abcissa represents the articles sorted by the average coefficient value r reported}.
Shown here are the \textcolor{red}{"raw} dataset" (recorded at both interspecific
and intraspecific level and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
is proportional to its weights in the meta-analysis. The colors
correspond to the stage for which the r values have been recorded: red
points corresponds adult stage, orange points to saplings, and grey
points to juveniles. the \textcolor{red}{The x abciss represents the study ID} }
\label{FigA4}
\end{figure}

>>>>

\item 
Traits should influence growth in a way that depend on individual plants size. We outline mechanisms and hypotheses based on new theory, and test these predictions in tree species for five traits using a meta-analysis of 112 studies (> 500 correlations).

@@

Meanwhile the possibility has been raised that trait-growth correlations may change systematically with size \citep{Falster:2011ii, Ruger:2012jv, Iida:2014ep, Iida:2014hq}.ADD REF  Recent theory suggests that the absence of a correlation between SLA and growth at larger sizes may be expected, when potential influences of traits on plant function are considered \citep{Falster:2011ii, falster:2013}. At larger sizes the low-cost deployment benefits of high SLA may be offset or even outweighed by the high costs of rapid leaf turnover (see Text Box 1\ref{sec:growth}).

Here, we review published literature reporting on relationships between plant growth and five prominent traits (specific leaf area = SLA, wood or stem tissue density = WD, maximum leaf photosynthetic capacity per unit area = Aarea,  maximum height= Hmax, and seed mass= SM) in tree or woody species in order to assess the following questions.

@@

The main effect of increased seed size is to produce a larger overall seedling. Generally relative growth rate decreases with size (REF Enquist et al 1999 Nature, Tilman 1988?), and as such larger seedlings are predicted to have a lower relative growth rate during the earliest phases of growth \citet{Turnbull:2012ew}. However, among larger plants we expect the effect of this initial size to be minimal, and thus the correlation between seed size and growth rate should disappear.

@@

\textbf{Effect on absolute (AbsGR) and relative growth rate (RGR}
Tree growth is the increase in dimensions (i.e. diameter, height or mass) of an individual tree through time. While plant functional traits measurements are standardized across plant ontogeny, plant growth is commonly expressed differently according to the plant size/stage considered. Thus, mass and height are both used for smaller plants, whereas height and diamater are more convenient measures for larger tree. In addition, the growth increment (i.e. rate of change of a dimension per unit time) can be expressed in either absolute or relative terms. Relative growth rate (RGR, the change in a dimension per time interval relative to initial size) is commonly used for smaller plants, but is less useful for larger-plants because there is a very rapid decline in RGR with increasing tree size due to accumulation of support tissues (bark, branches etc). According to the growth model, the correlation between trait and growth is predicted to revert according to the growth measurement used, for both SLA and seed mass (TABLE?). The predicted relationship between growth and either SLA or seed mass in seedlings differs if absolute growth rate in mass is used instead of $RGR_{mass}$ (i.e. becomes negative for SLA, positive for SM).

@@

We aimed to identify studies that measured the correlation between a functional trait and a growth measurement, and searched for relevant studies using a three step procedure. First, we identified traits for which a substantial number of studies would be available using a literature snapshot in Web of Science. While Web of Science guarantees a relatively stable and reproducible search environment, with clearly defined lists of indexed journals, its searches are restricted to metadata, such as title, keywords and abstracts \citep{Beckmann:2012hn}. This limitation does not apply to Google Scholar, where, theoretically, all text that is electronically available on the Internet will be indexed. Thus, our second step was to systematically read documents returned by Google scholar for a restricted set of traits. Finally, we identified and recorded other possible data sources using our own knowledge as researchers in the field (this included adding data from an as-yet unpublished study by Gleason et al). The complete list of studies where we inspected the full text is given in Appendix \ref{app:supp_info_files} in Supplementary material.

@@

We focused on an initial list of 20 traits (Fig. \ref{Fig1}) which capture different aspects of plant species strategies. Specific leaf area (SLA), leaf area, leaf nitrogen and phosphorus concentration, net (mass) assimilation rates (NAR), and assimilation rate of CO$_2$ (Aarea) are traits involved in species leaf economic strategy \citep{Wright:2004jb,Wright:2010tp}. Seed mass (SM), and maximum plant height (Hmax) capture information about reproductive strategy \citep{Falster:2005bw,Moles:2006ft}. Wood density (WD) and sapwood area per leaf area (SA/LA), vessel size and density, and stem specific conductance are all involved in species wood economic strategy \citep{Chave:2009iy}. Here WD and SA/LA are also considered as indicators of stem construction cost \citep{Falster:2011ii}, whereas SLA and leaf thickness capture crucial information about leaf construction cost \citep{Wright:2004jb}. Finally, the leaf area ratio and leaf mass ratio are indicators of resource allocation to leaf \citep{Lambers:1992bj}. We used the literature snapshot to identify traits which i) were most likely to return a substantial number of articles , and ii) shared a large proportion of their literature list with other traits. The Web of Science database (Thomson Reuters) was searched between March and June 2014 using a range of Boolean search terms in English. Search terms were as follows: (``NAME'' AND (``growth rate'' OR ``relative growth rate'')) AND (``tree*'' OR ``woody*''), ``NAME'' was one of trait names listed in

@@

While it would be more appropriate to address plant size as a continous variable, the limited quantity of data available in the literature steered us to focus on plant size as a categorical variable (i.e. plant stages). The authors of the 112 articles reported in our meta-analyses, categorized plants into four differents stages (i.e. seedling, juvenile, sapling, adult). They also reported plant size informations in diameter, height or age; generally the authors give the size of the smallest and the biggest plants species used in their analyses. While the stage categories have been established according to the expertise and the appreciation of the authors, by compiling data across multiple studies and across different growth form (tree, woody, etc), there is a risk of assigning plants of similar size to different categories. Thus, we tested how consistent were the range values in size/age attributed to each stage across the 112 studies, and across the different growth form (tree, woody and across growth form, Fig. A1). Suprisingly, the threshold in size/age used by the authors to defined a plant stage are quite steady across the 112 studies (Fig. A1). In particular, there was a clear break between seedlings and saplings in both age (at 1 yr) and height (at 0.5 m); there was also a clear break between saplings and adults in diameter (at 10 cm). The distinctions between sapling-adult in age (around 5 yrs) and height (around 2 m), and between seedling-sapling in diameter (around 1cm) were less pronounced. We used simple allometric relationships from the Biomass And Allometry Database (BAAD) \citep{Falster:2015} to ensure that these size/stage cutoffs match across the different size measurements (i.e. diameter, height and age, Fig. A2). For instance, we showed according to BAAD that a sapling with a diameter < 10 cm would have a height < 1 m. Thus, according to the size/stage threshold established across 112 studies, the plant will be assigned to the sapling stage whatever we focused on its diamter or height (see Fig. A2 c).

There were an ambiguity on the plant stage attribution for less than 5\% of the studies (i.e. 5 studies on 112). We re-red carefully each of these studies, looking at any particular reason addressed by authors that could explained these discrepancies. Interestingly, these discrepancies were not due to a differences between growth form; all the ambiguous cases corresponds to studies focusing exclusively on tree species (Fig. A1). In fact, we identified two main explanations. First, the term "juvenile" was vague enough to cover either seedling or sapling stages according to the authors. Second, the reproductive state of a plant is not strictly correlated to plant size; some plants with a large stature are not assessed as adult because the authors selected them to be non reproductive (See ID 50, 52 and 105 in Fig. A1). Thus, we attributed a study to a new stage category when 95\% of the recorded range of sizes for that study lay within a new category. And, we attributed a study to the adult stage when the authors identified the plants as reproductive regardless the plant size or age. The size/stage threshold defined across the 112 articles, allowed us to attribute straightforwardly a stage category to studies for which no stage have been distinctly mentionned by the authors (5\% of the data, noted as 'mix' in Fig. A1). Finally, we run the analyses with both the old and the standardized categories to ensure that the different stage attribution will not disturb our results.

Results using the categories established by the authors are similar than the one using the standardized categories and are available in Fig. A8. In the main text, we report the results using the standardized categories. In the rest of the mansucript, we preferred the term "juvenile" to "seedling", because for a portion of the scientific community "seedling" also refers to a particular experimental condition (a greenhouse experiment).

@@

We tested size/stage effect on traits for which > 15 correlation coefficients across at least two stages were recorded. We used a mixed-effect model of meta-analysis, in which it is assumed that studies within a stage share a common mean effect but that there is also random variation among studies in a stage, in addition to sampling variation. This random effect allows us to account for the heterogeneity among studies (e.g.~experimental type, vegetation type, error, etc.). For each trait, we established if stage could explain variance in the coefficient correlation by comparing models with the stage variable to the null model using log-likelihood ratios \citep{Zuur:2009cfa}. If the log-likelihood test returned a significant p-value, the stage model fitted the data better than the null model. Effects of other variables (vegetation type, experiment type and growth measurement) were also tested individually (results shown in the Fig. A8). Estimates of the effect size for each stage were considered significant if the 95\% confidence intervals did not overlap with zero. In the case of multiple comparisons within a study, we used the method proposed by \citet{Borenstein:2009um}: we calculated the mean correlation coefficient by trait and by study, and re-calculated the effect size. Finally, we checked the dataset for publication bias with funnel plots (\citealt{Koricheva:2013tz}, Fig. A9). A publication bias toward significant results creates an asymmetric funnel with small studies with non-significant effects missing from the mouth of the funnel on the side opposite to the true effect. In addition, to avoid publication bias due to selective reporting of significant results within published articles (e.g.~particular case of a 'failure to publish bias' see \citealt{Jennions:2013ta}), we asked the authors for additional information when they reported a non-significant correlation between growth and trait without reporting an r value.

@@

For both SLA and SM, the correlation between growth rate and the trait changed significantly with plant size in the manner expected. Model fits improved when stage was incorporated (see log likelihood ratio tests, Fig. \ref{Fig2} a and d; average values for the coefficients r ($r_{\textrm{mean}}$) in Fig. A5). The correlation between growth and SLA shifted from strongly positive at juvenile stage $r_{\textrm{mean}}=0.6 \pm 0.08$, Mean +SD) to not significantly different from zero at adult stage ($r_{\textrm{mean}}= -0.01 \pm 0.07$, CI 95\% overlapping zero in Fig. \ref{Fig2} a). The correlation between growth and SM shifted from negative at juvenile stage ($r_{\textrm{mean}}= -0.59 \pm 0.07$) to not significantly different from zero at adult stage ($r_{\textrm{mean}}= -0.09 \pm 0.02$, , CI 95\% overlapping zero in Fig. \ref{Fig2} d). For both traits,  correlation coefficients recorded at sapling stage were intermediate between juvenile and adult stages.

@@

Given our basic conclusion that reported correlations responded to plant size in a manner consistent with expectations from theory, we assess now the coverage of the available data, to determine if biased sampling could have erroneously generated the above results. The results reported were confined to correlations across species, and under non-stressed conditions (n=176). A "complete" dataset (n=216) also included correlations measured under stressed conditions, and spanning different plant stages between the growth and trait measurements. This "complete" dataset generated similar effect sizes to those reported above from the "ideal" dataset, and led to similar conclusions (Fig. \ref{Fig2} grey points). Differences concerned often the confidence intervals around particular mean effect sizes in Fig. 2. These differences in CI were not easily attributed to any single cause. For instance, the correlation between growth and WD at juvenile stage shifted from negative to non significant (i.e CI95\% included zero) due to 2 positive correlation coefficients from \citet{Augspurger:1984ct};  these correlations unlike others used wood density values from adult plants together with growth from juveniles. For Aarea, the comparison between complete and ideal data showed no signal of an effect of stress (here mainly low light) on the correlation with growth at seedling stage; the correlation was still positive between Aarea and growth even when 7 correlations measured under low light conditions were added. Finally, our results were unlikely to be biased by dominance of one or a few studies that measured a large number of responses, since when multiple responses were condensed into a single average within a trait and within a study, outcomes were very similar (Fig. A7).
While we were mainly interested by the relationships between traits and growth across species, around 9 percent of the litterature reports a correlation measured within species. The number of correlations recorded is too few to test our hypotheses at within species level. Yet, a 'raw' dataset (n=263) including correlations across and within species and under both non-stressed and all conditions generated similar results to those reported across species exclusively (Fig. A6).

@@

We found 112 studies published between between 1983 and 2014 that met our requirements. Climate zones spanned from temperate regions to  tropics (map in Fig. A3). Different experiment types (laboratory, field, plantation or greenhouse) and growth measurements were included (see Fig. A8 for analyses of how these factors affected  correlations between growth and traits). Given this variety, it was not surprising to find wide ranges of r reported for all traits. For instance,  r varied from -0.98 to 0.99 for SLA, and from -0.74 to 0.74 for WD (Fig. A4). Number of species used for each correlation ranged from 1 to 300 species with average  31. As expected the correlation coefficient varied less widely as sample size increased (funnel plots Fig. A9). In the analyses described in Figs 2, A5 and A6 coefficients were weighted according to sample size, making the small-sample extremes less influential. Funnel plots exhibited a typical funnel shape for all five functional traits analyzed, showing no evidence for publication bias (Fig. A9).

@@

The meta-analysis reported here demonstrates that the influence of traits on growth rates changes as plants grow from small to large, for several key traits. While this point has been made recently in smaller scale studies, it is the first time that mechanistic hypotheses are confirmed across a large number of studies. Meta-analysis allowed us to generalize about trait influences on growth using the literature already available on traits. Thus, plant growth rates change with size through ontogeny \citep{Condit:1993hd, Clark:1999ed, Herault:2011dd} - \textit{they follow a trajectory of growth} - and species traits should be understood as influencing this trajectory and consequently rearranging the ranking of growth rates with size, rather than as rendering species fast-growing or slow-growing throughout life.

@@

It has previously been noted that the correlation of SLA with growth disappears among saplings and larger trees (\citealt{Wright:2010tp} for Barro Colorado Island forest, Panama), and this meta-analysis generalises that result. Several authors have suggested that the disappearance of SLA's influence on growth might be due to a disproportionate accumulation of leaf area by low SLA species \citep{Reich:1992wm,Poorter:2008iu,Wright:2010tp}, yet it remain uncear whether such a mechanism works as intended. More importantly, the assumed empirical relationship between SLA and total leaf area does not hold true across large number of species (Duursma and Falster, in review).In the model described here, the mechanism is slightly different: high-SLA species incur faster leaf and other tissues turnovers, the cost of which outweighs the benefits of cheap leaf construction at larger sizes.

@@

\begin{figure}[htbp]
\centering
\includegraphics{output/Fig1.pdf}
\caption{Number of correlations between trait and growth for each plant stage recorded in our dataset. Shown here are 'raw dataset' (recorded both across and within species, under unstressed and stressed conditions). Bar colors: red for adult, orange for sapling, grey for juvenile. Aarea (or Amass) = rate of $CO_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax= asymptotic maximum height,  Ks =stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea (or NARmass) = net mass assimilation rate per unit of leaf area (or leaf mass), Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, thickness = leaf thickness, Vessel size = stem conduit size, vessel density = stem conduit density, WD = wood density}
\label{Fig1}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/Fig2.pdf}
\caption{The relationship between growth rates and SLA or seed mass changes with plant stage. Plots show the effect size (+ 95\%CI) of the correlation across species between growth rate and five functional traits for plant stage comparisons. \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Asymptotic height (Hmax) \textbf{d)} Seed mass and \textbf{e)} Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if confidence intervals (95\%CI) for a given stage do not overlap with zero. Shown here are 'across species dataset' (recorded only across species, and under both unstressed and stressed conditions). Black point: unstressed conditions, grey points: all the data. 'n' indicates number of correlations contributing to each effect. Likelihood Ratio Tests (LRT, for unstressed conditions only) compared maximum-likelihood fits between a pooled model and one separated by stage. A significant p-value means the stage model fitted the data better than the null model. 
}
\label{Fig2}
\end{figure}

@@

"code.zip": the data and analysis code used to generate the results in this paper. A copy of the complete data set is also available from the Dryad Digital Repository.

@@

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA1.pdf}
\caption{Range of plant size in \textbf{a)} age, \textbf{b)} height and \textbf{c)} diameter and the plant stage assigned by the authors of the articles used in the meta-analyses. Each segment represents the plant size range (max and min values) of the species used to measure the correlation between growth and traits in each article. ID is the reference number of the article in our dataset. The colors represents the stage information given by the authors (green: seedling, blue: juvenile, orange: sapling, red: adult, grey: unspecified by the authors), the vertical line represents the most likely limits between stage categories, the horizontal line styles corresponds to the species growth form used in each study (solid line: exclusively tree, dashed line: woody species , dotted line: tree mixed with another growth form). Shown here are the "raw dataset" (recorded both across and within species, and under unstressed and stressed conditions).}
\label{FigA1}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA2.pdf}
\caption{Allometric relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height in trees according to the BAAD database. Green and red lines are the cutoffs between stage categories used in the literature. Green lines corresponds to limits between juveniles and saplings, red lines to limits between saplings and adults.}
\label{FigA2}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA3.pdf}
\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis. Shown here are the "raw dataset" (recorded both across and within species, and under unstressed and stressed conditions).}
\label{FigA3}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA4.pdf}
\caption{Range of correlations (r) between
growth and trait reported in the literature (112 articles). Plots shown the coefficients of correlation (r)
between the plant growth and \textbf{a)} Specific leaf area (SLA, n=
111), \textbf{b)} Wood density (WD, n=64), \textbf{c)} Asymptotic
maximum height (Hmax, n=23), \textbf{d)} Seed mass (Seedmass, n=36 and
\textbf{e)} Rate of CO2 assimilation (Aarea, n=24) reported from 112
articles. The x abcissa represents the articles ID sorted by the average coefficient value r reported.
Shown here are the "raw dataset" (recorded both across and within species
and under unstressed and stressed conditions). Each bubble represents a r value, the diameter of the bubble
is proportional to its weights in the meta-analysis (i.e. number of species used). The colors
correspond to the stage for which the r values have been recorded: red
points corresponds adult stage, orange points to saplings, and grey
points to juveniles.}
\label{FigA4}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{output/FigA5.pdf}
\caption{\textbf{Mean coefficient correlation r (+SD) between growth rate and traits, established from 112 articles.} The mean coefficients are weighted by sample size (i.e number of species used to perform the correlation), and calculated both across all plant stages and for each stage. Each panel corresponds to a functional trait: \textbf{a)} Specific leaf area (SLA), \textbf{b)} Wood density (WD), \textbf{c)} Net assimilation rate (NARarea), \textbf{d)} Seed mass, \textbf{e)} Asymptotic height (Hmax) and \textbf{f)} Assimilation rate of CO2 (Aarea). Shown here are the "unstressed dataset" (recorded across species and under unstressed conditions).}
\label{FigA5}
\end{figure}
